Printer ballistics through character's texture analysis

### 2013-11-19 Printer_Ballistics.tex
Related works

Literature on the identification of printing devices from their printed documents is not wide in Academia. The work of Kee et al \cite{Printer_Profiling} reports a technique of geometric modeling of degradation caused by the printer. According to the authors, this degradation, measured based on a character basis, is modeled constructing a linear basis from characters commonly found on a printed page. From the point of view of ballistics, the accuracy of the developed technique allows to identify the device that originated the printed pages. According to the authors, the technique allows to distinguish between printers of different brands and models, but not among printers of the same make and model.

@@

Valuable is also the work of Rocha and Leite \cite{Rocha}. This work deals with the concept of analysis of textures through the co-occurrence matrix, used as a cornerstone of the solution proposed by us.

@@

Using an example similar to the rotated character, we can compare the value differences in the properties obtained from the co-occurrence matrix (Figure \ref{fig:characters_angle}). In this case, the character on the left was obtained directly from the scanned document, the character on the right is the same character, but rotated -4º.

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Discussion}

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}

>>>>

Literature on the identification of printing devices from their printed documents is not wide in Academia. The work of Kee and Farid \cite{Printer_Profiling} reports a technique of geometric modeling of degradation caused by the printer. According to the authors, this degradation, measured based on a character basis, is modeled constructing a linear basis from characters commonly found on a printed page. From the point of view of ballistics, the accuracy of the developed technique allows to identify the device that originated the printed pages. According to the authors, the technique allows to distinguish between printers of different brands and models, but not among printers of the same make and model.

@@

The work of Pollard et al \cite{Pollard} presents a general method for extracting a signature print from the outer boundary of a text glyph.

Valuable is also the work of Rocha and Leite \cite{Rocha}. This work deals with the concept of analysis of textures through co-occurrence matrix, used as a cornerstone of the solution proposed by us.

@@

Using an example similar to the rotated character, we can compare the value differences in the properties obtained from the co-occurrence matrix (Figure \ref{fig:characters_angle}). In this case, the character on the left was obtained directly from the scanned document; character on the right is the same character, but rotated -4º.

@@

%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments and Discussion}
\label{sec:experiments}
%%% Add section %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}
\label{sec:conclusions}

\section{Acknowledgements}
\label{sec:acknownledgements}

We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.
